% !TEX root = ../Vorlage_DA.tex

%	########################################################
% 					Fazit und Persönliche Erfahrungen
%	########################################################



%	--------------------------------------------------------
% 	Überschrift, Inhaltsverzeichnis
%	--------------------------------------------------------
\chapter{Conclusion and Personal Experience}


%	--------------------------------------------------------
% 	Fazit
%	--------------------------------------------------------
\section{Conclusion}

In general the funcionality of utilizing the camera feed, using the ORB-\gls{slam} and the LSD-\gls{slam} to process the data have been implemented. A few things still need to be done to achieve the set goal at the beginning. The points that are not fully completed are:
\begin{itemize}
    \item
    Merging the maps of the ORB-\gls{slam} and the LSD-\gls{slam}
    
    \item
    Get a camera calibration which makes the LSD-\gls{slam} more detailed
    
    \item
    Get the DeepTAM working on a newer version of Linux and newer drivers
    
    \item
    A wrapper to use the DeepTAM in \gls{ros} as well
\end{itemize}
%	--------------------------------------------------------
% 	Persönliche Erfahrungen
%	--------------------------------------------------------
\section{Personal Experience}

Through this project we have gained a good insight into project planning and implementation of extensive practice-oriented projects. Especially in the area of project management we have developed a lot and also noticed how important it is to plan such projects ahead carefully before working on them. Furthermore we also learned to often test the implemented features and also to rework things if it does not produce the expected results. \newline

Due to good and clear division of tasks, problems could be avoided as far as possible. Also the communication within the team worked well for the most part and therefore only had minor problems in the implementation of the project. \newline

The interaction with the \textit{Johannes Kepler University - Artificial Intelligence Lab} worked very good and we got great support in our work by them. Therefore we want to thank you again for the unique opportunity and commitment. Furthermore we want to thank our project supervisor \textit{Dipl. Ing. Gerhard Müller} for the support and the establishment of contact to the Johannes Kepler University.